Turbulence in compact to giant HII regions

### 2022-04-18 strucfunc_paper.tex
Small advance on the model fit section

In order to provide a uniform description of the velocity fluctuations,
we fit the model structure function
\(\tilde{B}(r)\) of equation~\eqref{eq:sf-functional}
to each \hii{} region in our sample.
Results are shown in Figures~\ref{fig:strucfunc-fit-Galactic}, \ref{fig:strucfunc-fit-MC},
and \ref{fig:strucfunc-fit-ExtraGal}, arranged in order of increasing distance.

For the observational values (blue symbols),
the structure function is the average value of equation~\eqref{eq:Br}
over all pairs of points that contribute to each radial bin.
The uncertainty of each bin (blue error bars) is estimated
as the standard deviation of these values divided by the square root of
the number of contributing pairs.
For most sources a fixed bin size of \SI{0.05}{dex} is used,
but for those observed with multi-fiber spectroscopy
(Carina and M8, see section~\ref{sec:flames-multi-fiber}),
where coverage is sparse at small separations,
adjacent bins were merged to ensure at least 100 pairs contribute to each bin.
Bins with separation less than \(L/2\) are used to constrain the model fitting (filled symbols),
while larger separations (open symbols) are not used
since they are more likely to be affected by a breakdown
of the homogeneity assumption (see section~\ref{sec:limit-model-struct}).

Non-linear weighted least square fitting of the model is performed
using the Levenberg-Marquardt algorithm \citep{More:1978a} as implemented in the
\texttt{lmfit} Python library \citep{newville_matthew_2014_11813}.
The best-fit model \(\tilde{B}(r)\) is shown (heavy orange solid line),
together with the corresponding underlying ``true model'' \(B(r)\) (heavy dashed green line),
which does not include the effects of seeing or noise.
Note that the true model \(B(r)\) depends on only 3 parameters:
\(\sigma^2\), \(r_0\), and \(m\),
whereas \(\tilde{B}(r)\) additionally depends on
the observational nuisance parameters: \(s_0\) and \(B\noise\).
The best-fit values of each of these parameters are shown by
horizontal and vertical lines.

The posterior distributions of model parameters
that are consistent with the observations for each region are estimated
using Markov Chain Monte Carlo (MCMC) ensemble sampling \citep{2010CAMCS...5...65G}
as implemented in the \texttt{emcee} Python library \citep{2013PASP..125..306F}.
A uniform prior distribution is assumed between upper and lower bounds
for each parameter, as given in Table~\ref{tab:parameter-ranges}.
To help ensure convergence of the MCMC algorithm,
we used chain lengths that exceeded \num{50} times the
estimated autocorrelation length for each parameter,
which required \num{50000} to \num{150000} samples,
depending on the source.
Thin translucent lines in the figures show structure functions using the parameters of
a random selection of \num{100} posterior samples from the MCMC chain,
both for \(\tilde{B}(r)\) orange and \(B(r)\) (green).
This gives an estimate in the uncertainty about the best-fit model.
Credibility intervals for the parameters are estimated from percentiles
of the posterior distribution and are indicated in the figures by shaded gray boxes
around the best-fit parameter values
(heavy shading for 68\% interval; light shading for 95\% interval).

>>>>

In order to provide a uniform description of the velocity fluctuations,
we fit the model structure function
\(\tilde{B}(r)\) of equation~\eqref{eq:sf-functional}
to each \hii{} region in our sample.
Results are shown in Figures~\ref{fig:strucfunc-fit-Galactic}, \ref{fig:strucfunc-fit-MC},
and \ref{fig:strucfunc-fit-ExtraGal}, arranged in order of increasing distance.
Best-fit values for the model parameters,
together with 95\% credibility range,
are given in Table~\ref{tab:Res}.

\subsection{Technical details of the model fits}
\label{sec:techn-deta-model}

For the observational values (blue symbols),
the structure function is the average value of equation~\eqref{eq:Br}
over all pairs of points that contribute to each radial bin.
The uncertainty of each bin (blue error bars) is estimated
as the standard deviation of these values divided by the square root of
the number of contributing pairs.
\textit{But this is not true -- we use constant fractional error with adjustments for small and large separations.}
For most sources a fixed bin size of \SI{0.05}{dex} is used,
but for those observed with multi-fiber spectroscopy
(Carina and M8, see section~\ref{sec:flames-multi-fiber}),
where coverage is sparse at small separations,
adjacent bins were merged to ensure at least 100 pairs contribute to each bin.
Bins with separation less than \(L/2\) are used to constrain the model fitting (filled symbols),
while larger separations (open symbols) are not used
since they are more likely to be affected by a breakdown
of the homogeneity assumption (see section~\ref{sec:limit-model-struct}).

Non-linear weighted least square fitting of the model is performed
using the Levenberg-Marquardt algorithm \citep{More:1978a} as implemented in the
\texttt{lmfit} Python library \citep{newville_matthew_2014_11813}.
The best-fit model \(\tilde{B}(r)\) is shown (heavy orange solid line),
together with the corresponding underlying ``true model'' \(B(r)\) (heavy dashed green line),
which does not include the effects of seeing or noise.
Note that the true model \(B(r)\) depends on only 3 parameters:
\(\sigma^2\), \(r_0\), and \(m\),
whereas \(\tilde{B}(r)\) additionally depends on
the observational nuisance parameters: \(s_0\) and \(B\noise\).
The best-fit values of each of these parameters are shown by
horizontal and vertical lines in the figure and are summarised in Table~\ref{tab:Res}.

The posterior distributions of model parameters
that are consistent with the observations for each region are estimated
using Markov Chain Monte Carlo (MCMC) ensemble sampling \citep{2010CAMCS...5...65G}
as implemented in the \texttt{emcee} Python library \citep{2013PASP..125..306F}.
A uniform prior distribution is assumed between upper and lower bounds
for each parameter, as given in Table~\ref{tab:parameter-ranges}.
To help ensure convergence of the MCMC algorithm,
we used chain lengths that exceeded \num{50} times the
estimated autocorrelation length for each parameter,
which required \num{50000} to \num{150000} samples,
depending on the source.
Thin translucent lines in the figures show structure functions using the parameters of
a random selection of \num{100} posterior samples from the MCMC chain,
both for \(\tilde{B}(r)\) orange and \(B(r)\) (green).
This gives an estimate in the uncertainty about the best-fit model.
Credibility intervals for the parameters are estimated from percentiles
of the posterior distribution and are indicated in the figures by shaded gray boxes
around the best-fit parameter values
(heavy shading for 68\% interval; light shading for 95\% interval).
The 95\% credibility interval for each parameter and for each source
is also given in Table~\ref{tab:Res}.
Figure~\ref{fig:corner-example-Orion} gives an example for Orion of
the pairwise correlations in the posterior distributions of the model parameters,
plotted using the \texttt{corner} Python library \citep{2017ascl.soft02002F}.
Corresponding plots for the remaining sources are given in Appendix~\ref{sec:addit-covar-corn}.

\subsection{Results of model fitting}
\label{sec:results-model-fitt}
